Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models

### 2020-06-19 analysis/paper/paper.Rmd
updated the template to match ecological applications suggestions. Made a few minor revisions to text and figures, put each table and figure on it's own page, and re-knit into Word, PDF and html.

---
title: "Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@merck.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@merck.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    bookdown::html_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography:
- references.bib
- packages.bib
csl: "../templates/ecological-applications.csl" # Insert path for the bib-style
# csl: "../templates/canadian-journal-of-fisheries-and-aquatic-sciences.csl"
abstract: |
  **Might still need some refining...**
  Establishing robust methods and metrics to evaluate habitat quality is critical for the recovery of endangered Pacific salmonids. A variety of modeling approaches are used for status and trend monitoring of anadromous species throughout the Pacific Northwest, USA, but rely on linear fish-habitat relationships and are limited in predictive power beyond specific watersheds. Further, the focus on species distribution and abundance is not easily manipulated to predict carrying capacity and traditional stock-recruitment analyses are reliant on long-term data which are not always available. In this study, we developed a quantile random forest (QRF) model to  provide estimates of habitat carrying capacity for Chinook salmon parr during the summer months, at both the site and watershed scale. QRF models allow for the consideration of noisy data, correlated variables, and non-linear relationships: common features in fish-habitat datasets. We leveraged Columbia Habitat Monitoring Program (CHaMP) data to select habitat co-variates and predict capacity at those sites. We also identified a set of globally available attributes to extrapolate capacity estimate predictions throughout the Columbia River basin. Total capacity estimates for watersheds closely matched estimates from alternative fish productivity models. Carrying capacity estimates based on QRF, like those presented here, provide managers a framework to guide the identification, prioritization, and development of habitat rehabilitation actions to recover salmon populations.
keywords: |
  carrying capacity; quantile regression; random forests; Chinook; quantile regression forest
highlights: |
  These are the highlights. 
---

@@

```{r packages}
library(survey)
library(tidyverse)
# library(QRFcapacity) # for the moment, until we know exactly what data to copy over to this repo
library(QRFpaper)
library(janitor)
library(knitr)
library(pander)
library(magrittr)
library(sf)
library(english)
library(kableExtra)

@@

# panderOptions("big.mark", ',')

options(knitr.kable.NA = '-')
# options(knitr.table.format = "pandoc")
# options(knitr.table.format = "latex")

@@

sel_hab_mets %<>%
  left_join(hab_dict %>%
              select(Metric = ShortName,
                     Name) %>%
              distinct()) %>%
  mutate(Name = recode(Name,
                       'Wetted Width To Depth Ratio Avg' = 'Width:Depth Ratio',
                       'Wetted Depth SD' = 'Depth Complexity',
                       'Wetted Channel Braidedness' = 'Braidedness',
                       'Fish Cover: Total' = 'Fish Cover',
                       'Riparian Cover: Some Canopy' = 'Riparian Canopy',
                       'Wetted Width Integrated' = 'Wetted Width',
                       'Substrate < 6mm' = 'Fines',
                       # 'Substrate: D16',
                       'Avg. August Temperature' = 'Avg. August Temp.',
                       'Large Wood Volume: Wetted Slow Water' = 'Large Wood Freq. in Pools'))

@@

spawn_rec_comp_p = spawn_rec_params %>%
  # filter out a couple populations with super poor fits
  filter(Population %in% keep_wtsds) %>%
  select(Population, data) %>%
  unnest(cols = "data") %>%
  distinct() %>%
  ggplot(aes(x = Spawners,
             y = Parr)) +
  geom_polygon(data = cap_poly %>%
                 # filter out a couple populations with super poor fits
                 filter(Population %in% keep_wtsds),
              aes(x = x,
                  y = y,
                  fill = form),
              alpha = 0.2) +
  geom_line(data = curve_fits %>%
              # filter out a couple populations with super poor fits
              filter(Population %in% keep_wtsds),
            aes(color = form),
            lwd = 1.5) +
  geom_hline(data = cap_tbl %>%
               # filter out a couple populations with super poor fits
               filter(Population %in% keep_wtsds),
             aes(yintercept = est,
                 color = form),
             linetype = 2) +
  geom_point(size = 3) +
  facet_wrap(~ Population,
             scales = 'free') +
  scale_color_brewer(palette = 'Set1',
                     breaks = c('QRF',
                                'BevertonHolt',
                                'Ricker',
                                'Hockey'),
                     labels = c('QRF', 
                                'Beverton Holt',
                                'Ricker',
                                'Hockey Stick'),
                     name = 'Model') +
  scale_fill_brewer(palette = 'Set1',
                    breaks = c('QRF',
                               'BevertonHolt',
                               'Ricker',
                               'Hockey'),
                    labels = c('QRF', 
                               'Beverton Holt',
                               'Ricker',
                               'Hockey Stick'),
                    name = 'Model') +
  labs(shape = 'Spawner\nType') +
  theme(legend.position = 'bottom')

@@

```{r select-mets-table}
qrf_mod$importance %>%
  as_tibble(rownames = 'ShortName') %>%
  rename(imp = IncNodePurity) %>%
  arrange(desc(imp)) %>%
  mutate(Rank = 1:n()) %>%
  select(-imp) %>%
  left_join(hab_dict %>%
              select(-Name) %>%
              inner_join(sel_hab_mets %>%
                           rename(ShortName = Metric))) %>%
  filter(MetricGroupName != 'Tier 1 Summary') %>%
  select(Rank,
         Metric = Name,
         `Metric Category` = MetricCategory,
         Description = DescriptiveText) %>%
  kable(caption = "Habitat metrics and descriptions of metrics included in the QRF model to predict spring/summer Chinook salmon parr capacity (during summer months). Metrics are ranked in order of relative importance.",
        booktabs = T,
        format.args = list(width = c(2, 10, 10, 50))) %>%
  kable_styling() %>%
  column_spec(4, width = '3in')

@@

```{r gaa-covars}
tibble(Covariate = gaa_covars) %>%
  left_join(gaa_meta %>%
              select(Covariate = FieldName,
                     Name = DisplayName,
                     Units,
                     SpatialScale)) %>%
  mutate(Units = if_else(Units == "na",
                         as.character(NA),
                         Units),
         Units = if_else(grepl('\\^2', Units),
                         str_replace(Units, '\\^2', '$^2$'),
                         Units)) %>%
  mutate(Name = if_else(Covariate == 'S2_02_11' & is.na(Name),
                        'NorWeST Aug. Temperature',
                        Name),
         Units = if_else(Covariate == 'S2_02_11',
                                'C',
                                Units),
         SpatialScale = if_else(Covariate == 'S2_02_11',
                                'Reach-2km',
                                SpatialScale)) %>%
  left_join(model_svy_df$mod_full[[1]] %>%
              summary() %>%
              coefficients() %>%
              as_tibble(rownames = "Covariate") %>%
              select(1:3)) %>%
  select(-Covariate) %>%
  rename(`Spatial Scale` = SpatialScale,
         Covariate = Name) %>%
  kable(caption = "Globally available attribute (GAA) habitat covariates used to extrapolate quantile regression forest (QRF) model predictions of spring/summer Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.",
        booktabs = T, 
        escape = F,
        digits = 3) %>%
  kable_styling()

@@

```{r extrap-r2-table}
model_svy_df %>%
  ungroup() %>%
  mutate(n_full = map_dbl(data,
                          .f = nrow),
         k_full = map_dbl(mod_full,
                          .f = function(x) {
                            names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                              length
                          }),
         r_full = map_dbl(mod_full,
                          .f = function(x) {
                            cor(x$y, x$fitted.values)
                          }),
         r2_full = r_full^2,
         r2_adj_full = 1 - ( ( (1 - r2_full) * (n_full - 1) ) / (n_full - k_full - 1) )) %>%
  mutate(n_no_champ = map_dbl(data,
                              .f = nrow),
         k_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                                  length
                              }),
         r_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                cor(x$y, x$fitted.values)
                              }),
         r2_no_champ = r_no_champ^2,
         r2_adj_no_champ = 1 - ( ( (1 - r2_no_champ) * (n_no_champ - 1) ) / (n_no_champ - k_no_champ - 1) )) %>%
  select(response, starts_with("r2")) %>%
  gather(type, r2, -response) %>%
  mutate(model = if_else(grepl('no_champ', type),
                         'non-CHaMP',
                         'CHaMP'),
         type = if_else(grepl('adj', type),
                        'Adjusted R2',
                        'R2')) %>%
  spread(type, r2) %>%
  mutate(response = recode(response,
                           'chnk_per_m' = 'fish/m',
                           'chnk_per_m2' = 'fish/m$^2$')) %>%
  filter(response == "fish/m") %>%
  select(Model = model,
         Response = response,
         `$r^2$` = R2, 
         `Adjusted $r^2$` = `Adjusted R2`) %>%
  kable(caption = "Summary of extrapolation model fits, split by whether the extrapolation model used CHaMP watershed as a covariate or not.",
        escape = F,
        booktabs = T,
        digits = 3) %>%
  kable_styling()

@@

```{r sr-table}
spawn_rec_params %>%
  select(Population, data) %>%
  unnest(data) %>%
  group_by(Population) %>%
  summarise(`n Yrs` = n_distinct(BroodYear),
            Spawner_type = unique(Spawner_type)) %>%
  select(Population, `n Yrs`, Spawner_type) %>%
  mutate(Spawner_type = recode(Spawner_type,
                               'total spawners' = 'Spawners',
                               'redd counts' = 'Redds')) %>%
  rename(`Adult Data` = Spawner_type) %>%
  mutate(`Parr Data` = if_else(grepl('Chiwawa', Population),
                               'Parr Surveys',
                               'RST')) %>%
  full_join(spawn_rec_params %>%
              mutate(prnt_val = paste0(prettyNum(round(est), big.mark = ','), ' (', round(cv, 3), ')')) %>%
              select(Population, form, prnt_val) %>%
              mutate(form = recode(form,
                                   'BevertonHolt' = 'Beverton Holt',
                                   'Hockey' = 'Hockey Stick')) %>%
              mutate(form = factor(form,
                                   levels = c('Beverton Holt',
                                              'Ricker',
                                              'Hockey Stick',
                                              'QRF'))) %>%
              spread(form, prnt_val)) %>%
  filter(Population %in% keep_wtsds) %>%
  mutate(Population = recode(Population,
                             'Chiwawa R.' = 'Chiwawa River')) %>%
  kable(caption = "Estimates of parr capacity from both spawner-recruit data (Beverton-Holt, Ricker, hockey stick) and from extrapolated estimates of parr capacity from the quantile regression forest (QRF) model. Numbers in parentheses are coefficients of variation.",
        booktabs = T) %>%
  kable_styling() %>%
  # kable_styling(latex_options = c('scale_down')) %>%
  column_spec(1, width = "1in") %>%
  column_spec(c(5:8), width = "0.5in")

@@

```{r wtsd-map, fig.cap = "Watersheds with CHaMP habitat data. Watersheds in black also contain paired fish data. Watershed names are: 1 - Entiat, 2 - John Day, 3 - Lemhi, 4 - Methow, 5 - Minam, 6 - Secesh, 7 - South Fork Salmon, 8 - Tucannon, 9 - Upper Grande Ronde, 10 - Wenatchee, 11 - Yankee Fork."}
# knitr::include_graphics('../figures/ChampWtds.png')
knitr::include_graphics('../figures/ChampWtds.jpeg')
```

@@

```{r sr-figure, fig.cap = "Spawner-recruit data from nine watersheds. Solid lines are the spawner-recruit curve, dashed lines are the estimated capacity, and shaded polygons depict the 95% confidence intervals of capacity. Red corresponds to Beverton-Holt models, purple to Ricker models, blue to hockey stick models, and green to QRF estimates. The QRF solid curve is a Beverton-Holt model with the capacity parameter fixed to the QRF estimate of capacity."}

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

@@

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

>>>>

---
title: "Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@merck.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@merck.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    bookdown::html_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      # reference_docx: "../templates/EcologicalApplicationsTemplate.docx" # Insert path for the DOCX file
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      always_allow_html: true
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography:
- references.bib
- packages.bib
csl: "../templates/ecological-applications.csl" # Insert path for the bib-style
# csl: "../templates/canadian-journal-of-fisheries-and-aquatic-sciences.csl"
abstract: |
  Establishing robust methods and metrics to evaluate habitat quality is critical for the recovery of endangered Pacific salmonids. A variety of modeling approaches are used for status and trend monitoring of anadromous species throughout the Pacific Northwest, USA, but current methods often fail the capture the complex relationship between fish and habitat and are often limited in predictive power beyond specific watersheds. Further, the focus on species distribution and abundance is not easily manipulated to predict carrying capacity and traditional stock-recruitment analyses are reliant on long-term data which are not always available. In this study, we developed a quantile random forest (QRF) model to  provide estimates of habitat carrying capacity for Chinook salmon parr during the summer months, at both the site and watershed scale. QRF models allow for the consideration of noisy data, correlated variables, and non-linear relationships: common features in fish-habitat datasets. We leveraged Columbia Habitat Monitoring Program (CHaMP) data to select habitat co-variates and predict capacity at those sites. We also identified a set of globally available attributes to extrapolate capacity estimate predictions throughout the Columbia River basin. Total capacity estimates for watersheds closely matched estimates from alternative fish productivity models. Carrying capacity estimates based on QRF, like those presented here, provide managers a framework to guide the identification, prioritization, and development of habitat rehabilitation actions to recover salmon populations.
keywords: |
  carrying capacity; quantile regression; random forests; Chinook; quantile regression forest
highlights: |
  These are the highlights. 
---

@@

```{r packages}
library(survey)
library(tidyverse)
library(QRFpaper)
library(janitor)
library(knitr)
library(pander)
library(magrittr)
library(sf)
library(english)
library(kableExtra)

@@

options(knitr.kable.NA = '-')

# when knitting to Word, use this
# options(knitr.table.format = "pandoc")

@@

# change some of the names of metrics for plotting purposes
sel_hab_mets %<>%
  left_join(hab_dict %>%
              select(Metric = ShortName,
                     Name) %>%
              distinct()) %>%
  mutate(Name = recode(Name,
                       'Wetted Width To Depth Ratio Avg' = 'Width:Depth Ratio',
                       'Wetted Depth SD' = 'Depth Complexity',
                       'Wetted Channel Braidedness' = 'Braidedness',
                       'Fish Cover: Total' = 'Fish Cover',
                       'Riparian Cover: Some Canopy' = 'Riparian Canopy',
                       'Wetted Width Integrated' = 'Wetted Width',
                       'Substrate < 6mm' = 'Fines',
                       # 'Substrate: D16',
                       'Channel Unit Frequency' = 'Channel Unit\nFrequency',
                       'Avg. August Temperature' = 'Avg. August Temp.',
                       'Large Wood Volume: Wetted Slow Water' = 'Large Wood\nFreq. in Pools'))

@@

# scale the parr numbers for the plot
scale_parr = 100000

spawn_rec_comp_p = spawn_rec_params %>%
  # filter out a couple populations with super poor fits
  filter(Population %in% keep_wtsds) %>%
  select(Population, data) %>%
  unnest(cols = "data") %>%
  distinct() %>%
  mutate_at(vars(Parr),
            list(~ . / scale_parr)) %>%
  ggplot(aes(x = Spawners,
             y = Parr)) +
  geom_polygon(data = cap_poly %>%
                 mutate_at(vars(y),
                           list(~ . / scale_parr)) %>%
                 # filter out a couple populations with super poor fits
                 filter(Population %in% keep_wtsds),
              aes(x = x,
                  y = y,
                  fill = form),
              alpha = 0.2) +
  geom_line(data = curve_fits %>%
              mutate_at(vars(Parr),
                        list(~ . / scale_parr)) %>%
              # filter out a couple populations with super poor fits
              filter(Population %in% keep_wtsds),
            aes(color = form),
            lwd = 1.5) +
  geom_hline(data = cap_tbl %>%
               mutate_at(vars(est),
                         list(~ . / scale_parr)) %>%
               # filter out a couple populations with super poor fits
               filter(Population %in% keep_wtsds),
             aes(yintercept = est,
                 color = form),
             linetype = 2) +
  geom_point(size = 3) +
  facet_wrap(~ Population,
             scales = 'free') +
  scale_color_brewer(palette = 'Set1',
                     breaks = c('QRF',
                                'BevertonHolt',
                                'Ricker',
                                'Hockey'),
                     labels = c('QRF', 
                                'Beverton Holt',
                                'Ricker',
                                'Hockey Stick'),
                     name = 'Model') +
  scale_fill_brewer(palette = 'Set1',
                    breaks = c('QRF',
                               'BevertonHolt',
                               'Ricker',
                               'Hockey'),
                    labels = c('QRF', 
                               'Beverton Holt',
                               'Ricker',
                               'Hockey Stick'),
                    name = 'Model') +
  labs(shape = 'Spawner\nType',
       y = 'Parr (x100,000)') +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 3)) +
  theme(legend.position = 'bottom')

@@

```{r select-mets-table, eval = T}
qrf_mod$importance %>%
  as_tibble(rownames = 'ShortName') %>%
  rename(imp = IncNodePurity) %>%
  arrange(desc(imp)) %>%
  mutate(Rank = 1:n()) %>%
  select(-imp) %>%
  left_join(hab_dict %>%
              select(-Name) %>%
              inner_join(sel_hab_mets %>%
                           rename(ShortName = Metric)) %>%
              mutate(Name = str_replace(Name, '\n', ' '))) %>%
  filter(MetricGroupName != 'Tier 1 Summary') %>%
  select(Rank,
         Metric = Name,
         `Metric Category` = MetricCategory,
         Description = DescriptiveText) %>%
  kable(caption = "Habitat metrics and descriptions of metrics included in the QRF model to predict spring/summer Chinook salmon parr capacity (during summer months). Metrics are ranked in order of relative importance.",
        booktabs = T,
        format.args = list(width = c(2, 10, 10, 50))) %>%
  kable_styling() %>%
  column_spec(4, width = '3in')

@@

```{r gaa-covars, eval = T}
tibble(Covariate = gaa_covars) %>%
  left_join(gaa_meta %>%
              select(Covariate = FieldName,
                     Name = DisplayName,
                     Units,
                     SpatialScale)) %>%
  mutate(Units = if_else(Units == "na",
                         as.character(NA),
                         Units),
         Units = if_else(grepl('\\^2', Units),
                         str_replace(Units, '\\^2', '$^2$'),
                         Units)) %>%
  mutate(Name = if_else(Covariate == 'S2_02_11' & is.na(Name),
                        'NorWeST Aug. Temperature',
                        Name),
         Units = if_else(Covariate == 'S2_02_11',
                                'C',
                                Units),
         SpatialScale = if_else(Covariate == 'S2_02_11',
                                'Reach-2km',
                                SpatialScale)) %>%
  left_join(model_svy_df$mod_full[[1]] %>%
              summary() %>%
              coefficients() %>%
              as_tibble(rownames = "Covariate") %>%
              select(1:3)) %>%
  select(-Covariate) %>%
  rename(`Spatial Scale` = SpatialScale,
         Covariate = Name) %>%
  kable(caption = "Globally available attribute (GAA) habitat covariates used to extrapolate quantile regression forest (QRF) model predictions of spring/summer Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.",
        booktabs = T, 
        escape = F,
        digits = 3) %>%
  kable_styling()

@@

```{r extrap-r2-table, eval = T}
model_svy_df %>%
  ungroup() %>%
  mutate(n_full = map_dbl(data,
                          .f = nrow),
         k_full = map_dbl(mod_full,
                          .f = function(x) {
                            names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                              length
                          }),
         r_full = map_dbl(mod_full,
                          .f = function(x) {
                            cor(x$y, x$fitted.values)
                          }),
         r2_full = r_full^2,
         r2_adj_full = 1 - ( ( (1 - r2_full) * (n_full - 1) ) / (n_full - k_full - 1) )) %>%
  mutate(n_no_champ = map_dbl(data,
                              .f = nrow),
         k_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                                  length
                              }),
         r_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                cor(x$y, x$fitted.values)
                              }),
         r2_no_champ = r_no_champ^2,
         r2_adj_no_champ = 1 - ( ( (1 - r2_no_champ) * (n_no_champ - 1) ) / (n_no_champ - k_no_champ - 1) )) %>%
  select(response, starts_with("r2")) %>%
  gather(type, r2, -response) %>%
  mutate(model = if_else(grepl('no_champ', type),
                         'non-CHaMP',
                         'CHaMP'),
         type = if_else(grepl('adj', type),
                        'Adjusted R2',
                        'R2')) %>%
  spread(type, r2) %>%
  mutate(response = recode(response,
                           'chnk_per_m' = 'fish/m',
                           'chnk_per_m2' = 'fish/m$^2$')) %>%
  filter(response == "fish/m") %>%
  select(Model = model,
         Response = response,
         `$r^2$` = R2, 
         `Adjusted $r^2$` = `Adjusted R2`) %>%
  kable(caption = "Summary of extrapolation model fits, split by whether the extrapolation model used CHaMP watershed as a covariate or not.",
        escape = F,
        booktabs = T,
        digits = 3) %>%
  kable_styling()

@@

```{r sr-table, eval = T}
spawn_rec_params %>%
  select(Population, data) %>%
  unnest(data) %>%
  group_by(Population) %>%
  summarise(`n Yrs` = n_distinct(BroodYear),
            Spawner_type = unique(Spawner_type)) %>%
  select(Population, `n Yrs`, Spawner_type) %>%
  mutate(Spawner_type = recode(Spawner_type,
                               'total spawners' = 'Spawners',
                               'redd counts' = 'Redds')) %>%
  rename(`Adult Data` = Spawner_type) %>%
  mutate(`Parr Data` = if_else(grepl('Chiwawa', Population),
                               'Parr Surveys',
                               'RST')) %>%
  full_join(spawn_rec_params %>%
              mutate(prnt_val = paste0(prettyNum(round(est), big.mark = ','), ' (', round(cv, 3), ')')) %>%
              select(Population, form, prnt_val) %>%
              mutate(form = recode(form,
                                   'BevertonHolt' = 'Beverton Holt',
                                   'Hockey' = 'Hockey Stick')) %>%
              mutate(form = factor(form,
                                   levels = c('Beverton Holt',
                                              'Ricker',
                                              'Hockey Stick',
                                              'QRF'))) %>%
              spread(form, prnt_val)) %>%
  filter(Population %in% keep_wtsds) %>%
  mutate(Population = recode(Population,
                             'Chiwawa R.' = 'Chiwawa River')) %>%
  kable(caption = "Estimates of parr capacity from both spawner-recruit data (Beverton-Holt, Ricker, hockey stick) and from extrapolated estimates of parr capacity from the quantile regression forest (QRF) model. Numbers in parentheses are coefficients of variation.",
        booktabs = T) %>%
  kable_styling() %>%
  # kable_styling(latex_options = c('scale_down')) %>%
  column_spec(1, width = "1in") %>%
  column_spec(c(5:8), width = "0.5in")

@@

```{r wtsd-map, fig.cap = "Watersheds with CHaMP habitat data. Watersheds in black also contain paired fish data. Watershed names are: 1 - Entiat, 2 - John Day, 3 - Lemhi, 4 - Methow, 5 - Minam, 6 - Secesh, 7 - South Fork Salmon, 8 - Tucannon, 9 - Upper Grande Ronde, 10 - Wenatchee, 11 - Yankee Fork."}
knitr::include_graphics('../figures/ChampWtds.png')
# knitr::include_graphics('../figures/ChampWtds.jpeg')
```

@@

```{r sr-figure, fig.height = 5, fig.cap = "Spawner-recruit data from nine watersheds. Solid lines are the spawner-recruit curve, dashed lines are the estimated capacity, and shaded polygons depict the 95% confidence intervals of capacity. Red corresponds to Beverton-Holt models, purple to Ricker models, blue to hockey stick models, and green to QRF estimates. The QRF solid curve is a Beverton-Holt model with the capacity parameter fixed to the QRF estimate of capacity. A few curves with high capacity estimates were not plotted to improve readability."}

@@

```{r colophon, cache = FALSE, eval = T}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

@@

```{r, eval = T}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
